### 2018-12-16 tex/paper.tex
Modified Pn Potts model to be diversity model now. Proof to be corrected.

\mysection{Accurate Submodular Extension for Higher-order Potts Model} The pairwise Potts model often fails
to capture useful image statistics because it restricts the order of the
potentials to be at most two. Higher order clique potentials can model complex
interactions of random variables, and thereby overcome this difficulty.

One of the higher-order models used in practice is the \textit{higher-order Potts} model \citep{kappes2016higher}. For this model, the clique potentials $\phi_c({\bf x})$ in 
the energy function (equation (\ref{eq:energy_hop_min})) are defined as

\begin{equation}
  \phi_c({\bf x}_c) = 
  \begin{cases}
    \gamma_0, &{\text{if}} \; \forall i, j \in c: x_i = x_j, \\
    \gamma_1, &{\text{else}}. 
  \end{cases} 
\end{equation}

The higher-order Potts model differs from the $P^n$ Potts model \citep{kohli2007p3} in that the penalty for homogeneous labelings $\gamma_0$ is invariant to the label, that is, does not depend upon the label. We found this invariance property important in deriving the submodular extension from the LP relaxation.

\myparagraph{LP Relaxation}
We state the LP relaxation of the MAP estimation problem for higher-order Potts model. Let us assume the pairwise potentials in equation (\ref{eq:energy_hop_min}) to be Potts model. Also, we use the same set of indicator variables as for the Potts model. The following is an accurate LP relaxation for the higher-order Potts model:

\begin{align}
    \text{(HOP-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a = 1}^N
    \sum_{i = 1}^L \phi_a(i)y_{ai} + 
    \sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    & + \quad \sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:hop-lp}
\end{align}

The objective function is similar to that for the Potts model along with the addition of terms corresponding to higher-order potentials.The constraints for (HOP-LP) are the same as for (P-LP). To the best of our knowledge, the above LP relaxation does not have worst-case tightness guarantee, hence the submodular extension we derive using it does not have worst-case optimality property.

\myparagraph{LP-based Submodular Extension} We use the same $1-of-L$ encoding
scheme as for Potts model. Problem \ref{eq:min_upper_bound} then factorises as:

@@

%Same as eq 5.6
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
where $f(.)$ is the Lovasz extension of $F(.)$. We are interested in making
this LP same as the (), thereby enabling us to recover the submodular extension
for higher-order Potts. The following proposition gives us the submodular
extension.
{\proposition The Lovasz extension of the following submodular extension for
  higher-order Potts model:
  \begin{align}
      F_{HOPotts}(A) &= F_{Potts}(A) + \nonumber \\
        &\sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
is the objective function $E({\bf y})$ of the LP relaxation (HOP-LP).
\label{proposition:hop_extension}}
\newline
We note that the component of the submodular extension corresponding to cliques is of the form of maximum of cut function (that are submodular) over all pairs in a clique. In general, maximum of submodular functions is not submodular. However, in our particular case, the maximum turns out to be submodular as shown in the proof below.

>>>>

\mysection{Accurate Submodular Extension for Higher-order Diversity Model} The pairwise Potts model often fails
to capture useful image statistics because it restricts the order of the
potentials to be at most two. Higher order clique potentials can model complex
interactions of random variables, and thereby overcome this difficulty.

A higher-order model useful in real-world applications is the \textit{diversity} model, that favours labeling where superpixels have fewer number of unique labels. As an example from semantic segmentation, it is preferable to have pixels belonging to a superpixel to be incorrectly labeled with two class labels rather than three or more class labels. Let $\Gamma({\bf x_c})$ be the set of unique labels assigned to variables in the clique $c$, and $\omega_c$ be the weight associated with the clique. In our case, we take the clique potentials as proportional to the number of unique labels in the clique $c$:

\begin{equation}
  \phi_c({\bf x}_c) = \omega_c|\Gamma({\bf x_c})|
\end{equation}
where the notation $|A|$ denotes the cardinality of a set A.

\myparagraph{LP Relaxation}

First, let us consider the IP formulation of the MAP problem for our diversity model. Using the same set of indicator variables $y_{ai} = \{0, 1\}$ as for the Potts model, which are binary now, the clique potential $\phi({\bf x_c})$ can be represented as

\begin{equation}
  \phi_c({\bf x}_c) = \omega_c \sum_{i = 1}^L \max_{(a, b) \in c} \cdot |y_{ai} - y_{bi}| 
\label{eq:hod_ip}
\end{equation}

For example, let the set of unique labels in a clique be $\Gamma = \{l_1, l_2, l_3\}$. This implies that $y_{ai} = 1$ for some, but not all, variables in the clique for $i = \{1, 2, 3\}$. Hence, $|y_{ai} - y_{bi}| = 1$ for some pairs $(a, b) \in c$ for $i = \{1, 2, 3\}$. Also, for any other label $i$, $|y_{ai} - y_{bi}| = 0$ for all $(a, b) \in c$ since $y_{ai} = 0$ for all variables $a$ for these labels $i$. For binary variables, the maximum possible value of $|y_{ai} - y_{bi}|$ is 1. Hence,$\phi_c({\bf x}_c) = \omega_c \cdot (1 + 1 + 1) = 3 \cdot \omega_c = \omega_c |\{l_1, l_2, l_3\}$|.

Equation (\ref{eq:hod_ip}) suggests that our diversity model can be interpreted as sum of $P^n$ Ising models over all labels. The $Pn$ Ising model corresponding to label $i$ is $\max_{(a, b) \in c} \cdot |y_{ai} - y_{bi}|$ and it imposes a penalty of 0 if all variables in clique $c$ take the same label $i$, else the penalty is 1.

We now relax the indicator variables $y_{ai}$ to lie in $[0, 1]$. Assuming the pairwise potentials in equation (\ref{eq:energy_hop_min}) to be Potts model, an accurate LP relaxation for the higher-order diversity model is given by:

\begin{align}
    \text{(HOD-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a = 1}^N
    \sum_{i = 1}^L \phi_a(i)y_{ai} + 
    \sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    & + \quad \sum_{c \, \in {\mathcal C}} \frac{w_c}{2} \sum_{i = 1}^L \max_{(a, b) \in c} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:hop-lp}
\end{align}
where the label (HOD-LP) stands for LP relaxation for higher-order diversity model. The objective function is similar to that for the Potts model along with the addition of terms corresponding to higher-order potentials. The constraints for (HOD-LP) are the same as for (P-LP). To the best of our knowledge, the above LP relaxation does not have worst-case tightness guarantee, hence the submodular extension we derive using it does not have worst-case optimality property.

\myparagraph{LP-based Submodular Extension} We use the same $1\text{-of-}L$ encoding
scheme as for Potts model. Problem \ref{eq:min_upper_bound} then factorises as:

@@

%Same as eq 5.6
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
where $f(.)$ is the Lovasz extension of $F(.)$. We are interested in making
this LP same as (HOD-LP) of equation (\ref{eq:hop-lp}), thereby enabling us to recover the submodular extension
for higher-order diversity model. The following proposition gives us the submodular
extension.
{\proposition The Lovasz extension of the following submodular extension for
  our higher-order diversity model
  \begin{align}
      F_{HOD}(A) &= F_{Potts}(A) + \nonumber \\
        &\sum_{c \in {\mathcal C}} \frac{w_c}{2} \sum_{i = 1}^L \max_{(a, b) \in c} [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
is the objective function $E({\bf y})$ of the LP relaxation (HOD-LP).
\label{proposition:hod_extension}}
\newline
We note that the component of the submodular extension corresponding to cliques is of the form of maximum of cut function (that are submodular) over all pairs in a clique. In general, maximum of submodular functions is not submodular. However, in our particular case, the maximum turns out to be submodular as shown in the proof below.
